\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This project focuses on the design and development of \textbf{FinPulse}, an
intelligent financial analysis platform intended to support investors in evaluating
investment decisions. The proposed solution relies on official SEC 10-K filings in
order to compare investment assumptions with the risks and facts disclosed by listed
companies in their regulatory reports.

FinPulse combines a data ingestion pipeline, a PostgreSQL database extended with
PGVector, textual embeddings, and a Retrieval-Augmented Generation mechanism to
retrieve relevant sections from financial documents. The platform also introduces a
coherence score, called NCI, which helps assess the level of risk and consistency
between a company's public narrative, its regulatory disclosures, and the user's
investment strategy.

The platform provides three main features: an analysis chatbot able to answer
financial questions and generate structured strategy reports, an automated monitoring
module for saved investment strategies, and a real-time watchlist displaying market
variations, alerts, sentiment shift indicators, and NCI score evolution. The adopted
architecture combines Angular for the user interface, Spring Boot for business
orchestration, FastAPI/Python for data processing, and PostgreSQL, PGVector and Redis
for persistence and performance.

This work therefore establishes a functional and technical foundation for a more
reliable, explainable and personalized financial decision-support platform, based on
official data sources and artificial intelligence.

\textbf{Keywords:} FinPulse, financial analysis, artificial intelligence, SEC, 10-K
filing, RAG, PGVector, NCI, Spring Boot, Angular.
